Look, we can do something

### 2024-10-22 paper.tex
Bottle neck -> bottleneck

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottle necks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottle neck and have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottle neck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottle neck and points $A$ and $C$ do not form it. If you choose a
point $O$ which lies outside of the pore and travel along the pore's boundary in
one direction (either clockwise or counter-clockwise), when you arrive at $A$
you will see the point $O$ to your left and when you are in $B$ you will see $O$
to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
the same side from you. Instead of doing this check for ``bottle-neckness'', we
add a penalty coefficient to the distance between points, namely for a pair of
points $(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$, called ``\highlight{awesomeness}'', using \ref{eq:intro}:
\begin{equation}
  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
  \label{eq:awesomeness}
\end{equation}
Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottle neck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}

>>>>

\section{A new pore shape parameter}
We propose a new parameter for shape description which is based on the idea of
numerical assession of bottlenecks in pores. For simplicity, we will assume
that our pore is 1-connected. Suppose you have a round pore in the form close to
a disk and another pore in the form of a dumbbell. We want to develop a
parameter which would be close to 1 for the first pore and close to 0 for the
second. For this purpose we want to visit all points which lie on the pore's
boundary and find a pair of points which form a bottleneck and have a small
distance between each other. Obviously, not all pairs of points which are close
to each other form a bottleneck. Namely, on \cref{fig:parameter} points $A$ and
$B$ form a bottleneck and points $A$ and $C$ do not form it. If you choose a
point $O$ which lies outside of the pore and travel along the pore's boundary in
one direction (either clockwise or counter-clockwise), when you arrive at $A$
you will see the point $O$ to your left and when you are in $B$ you will see $O$
to your right (or vice-versa). But if you are at $A$ or $C$ you will see $O$ to
the same side from you. Instead of doing this check for ``bottleneckness'', we
add a penalty coefficient to the distance between points, namely for a pair of
points $(A, B)$ we calculate the following:
\begin{equation}
  p_{AB} = \rho_{AB} / L_{AB}
  \label{eq:intro}
\end{equation}
where $\rho_{AB}$ is the Euclidean distance between $A$ and $B$ and $L_{AB}$ is
the length of a pore's boundary segment with end points $A$ and $B$ (there are
two such segments, you need to take the segment with minimal length). Suppose
$B$ is a set of all points on the pore's boundary. We define a new pore shape
parameter $p$, called ``\highlight{awesomeness}'', using \ref{eq:intro}:
\begin{equation}
  p = \inf \{p_{AB} \ \forall (A, B) \in B^2\}
  \label{eq:awesomeness}
\end{equation}
Obviously, it's unlikely that $p$ = $p_{AC}$ because $L_{AC} \approx \rho_{AC}$.
It's easy to see that $0 \le p \le 1$ because $0 \le \rho_{AB} \le L_{AB}$ for
any $A$ and $B$ for a line segment which connects $A$ and $B$ is the shortest
of all other curves which connect those points.
\begin{figure}
  \centering
  \includegraphics[width=0.9\linewidth]{images/parameter.png}
  \caption[]{A dumbbell-like boundary of a pore. Points $A$ and $B$ form a
    bottleneck while points $A$ and $C$ do not. This can seen by a relative
    position of the point $O$ while traversing the boundary
    counter-clockwise. Namely, it's on the left side when crossing $A$ but on
    the right side when crossing $B$. When crossing $A$ and $C$, the relative
    position of $O$ does not change. The parameter $p_{AB}$ is equal to the
    distance between $A$ and $B$ divided by length of the blue contour $L$.}
  \label{fig:parameter}
\end{figure}
